%%% Document class (e.g. article, letter, beamer, etc...)
\documentclass[12 pt]{article}
%%%

%%% Packages
\usepackage[round]{natbib} %Allows custom options for bibliography management
\usepackage{cite} %Adds bibliograhy functionality like \citet
\usepackage{geometry} %Allows me to set the margins
\usepackage{amsmath} %Adds additional math-related commands
\usepackage{amsfonts} %Adds fonts-within-math-mode functionality
\usepackage{amsthm} %Enables custom theorem environments
\usepackage{bm} %Adds bold math fonts
\usepackage{setspace} %Enables \doublespacing command
\usepackage{parskip} %Removes indentation
\usepackage{tikz} %Used for formatting plots and figures
\usepackage{float} %Used to force the position of tables and figures
\usepackage{graphicx} %For including images
\usepackage[T1]{fontenc} %Allows for encoding of slavic letters
\usepackage{lmodern} %Need to load back the original font for when T1 encoding is active
\usepackage{hyperref}
\usepackage{subcaption}
%%%

%%% Set the margins of the document
\geometry{
	left=1in,
	right=1in,
	bottom=1in,
	top=1in,
}
%%%

%%% NOTE: PLOT DIMENSIONS SHOULD BE AROUND 10 x 4

%%% User-defined commands

\DeclareMathOperator*{\argmax}{argmax} % The argmax operator

\newtheorem{assumption}{Assumption} % Treating assumptions like theorems.
\newtheorem{proposition}{Proposition} % Treating propositions like theorems.
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

% Footnote without superscripts --- used in title
\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

%%%

%%% Title
\title{Identification in a $2\times2$ occupational and matching
	model}
%\author{Sean M. T. Elliott\blfootnote{University of Toronto, sean.elliott@mail.utoronto.ca}}
\date{}
%%%


\begin{document}
	
	\maketitle
	
	\onehalfspacing
	
	\vspace{-2cm}
	
	\section{Preliminaries}
	

Consider a labour market with two occupations, managers whose skills are high and low, $M=\{H,L\},$ and workers whose skills are also high and low, $\omega=\{h,l\}$. There is a measure 1 of labor market participants.Every participant has an managerial skill, $M$, and a worker skill, $\omega$. Every participant chooses the occupation which maximizes their income. The matrix distribution of occupational skills across participants is given below:%
\[
P(M,\omega)=%
\begin{array}
	[c]{ccc}
	& \omega=l & \omega=h\\
	M=L & p_{Ll} & p_{Lh}\\
	M=H & p_{Hl} & p_{Hh}%
\end{array}
\]
where
\begin{align}
	&  p_{Hh}+p_{hL}+p_{Lh}+p_{Ll}=1\\
	& p_{ij}   >0;i=L,H;j=l,h.
\end{align}
Each firm consists of a manager and a worker. They produce a unit of output to sell in the output market. The quality of the output, which is also the revenue of the firm, by a manager of skill $M$ and a worker of skill $\omega$ is $R(M,\omega\dot{)}$.
\begin{assumption}
	$R(M,\omega)$, revenue, is strictly
	increasing in the occupational skills of the firm.
	\label{a1}
\end{assumption}
\begin{assumption}
	$R(M,\omega)$, revenue, is max supermodular
	in occupational skills\footnote{When $R(i,j)$ is continuous in occupational
	skills, max supermodular is the same as supermodular.}	
	\begin{equation}
		R(H,h)+R(L,l)>2\max(R(H,l),R(L.h))
		\label{maxsupermodular}
	\end{equation}
		\label{a2}
\end{assumption}

Let managers (owners of the firms) hire workers in a competitive labor market for workers. Let the market earnings of a worker of skill $\omega$ be $w(\omega)$. The manager of skill $M$ will choose a worker to solve:
\begin{equation}
	\pi^{\ast}(M,w(\omega))=\max_{\omega}R(M,\omega)-w(\omega) \label{profit max}
\end{equation}
$\omega^{\ast}(M,w(\omega))$, also known as the matching function, is the worker who is optimally chosen by the manager:
\begin{equation}
	\omega^{\ast}(M)=\arg\max_{\omega}R(M,\omega)-w(\omega) \label{worker choice}
\end{equation}
As is well known, supermodularity implies that there will be positive assortative matching by occupational skills within each firm. Let $\pi^{\ast}(M,\omega^{\ast}(M))$ be the maximized profits of the manager $M$ and $w(\omega^{\ast}(M))$ be the maximized earnings of the worker in the firm:
\begin{equation}
	R(M,\omega^{\ast}(M\dot{)})=\pi^{\ast}(M\dot{)}+w(\omega^{\ast}(M\dot{)})
	\label{5}
\end{equation}
If a worker's skill, $\omega$, is chosen by two types of managers, his wage only depends on his skill $\omega$ and not which type of manager he is matched to. We make a similar argument for managers. If a manager of skill $M$ is
indifferent between two types of workers, her maximized profits is $\pi^{\ast}(M,\omega^{\ast}(M))$, independent of which type of worker she actually chooses.

Given their occupational skills, ($M,\omega)$, every participant will choose
the occupation which pays them the highest income:%

\begin{equation}
	O^{\ast}(M,\omega,\pi^{\ast},w^{\ast}),=\arg\max_{M,\omega}(\pi^{\ast
	}(M,\omega^{\ast}(M)),w^{\ast}(\omega)) 
	\label{occupational choice}
\end{equation}


Due to the competitive labour market assumption, for every active firm in the
industry, its revenue, $R(M,\omega^{\ast}(M\dot{)})$, is equal to the
maximized profits and its wage bill%

\begin{equation}
	R(M,\omega^{\ast}(M\dot{)}\dot{)}=\pi^{\ast}(M,\omega^{\ast}(M\dot{)}\dot
	{)}+w^{\ast}(\omega^{\ast}(M\dot{)}\dot{)} \label{6}%
\end{equation}


We will now derive the demand and supply of occupational skills for the
industry. Let $I^{\ast}(M,\omega,\pi^{\ast},w^{\ast})$ be an indicator
function which takes the value 1 if a participant of skill ($M,\omega)$
strictly chooses to be a manager, $\pi^{\ast}(M,\omega^{\ast}(M))>w^{\ast
}(\omega)$, and is zero otherwise. Note that for any managerial skill $M$,
there is at most two types of participant $(M,\omega)$ for which $I^{\ast
}(M,\omega,\pi^{\ast},w^{\ast})>0$. Let $\phi(M,\omega,\pi^{\ast},w^{\ast}%
)\in(0,1]$ if a participant of skill ($M,\omega)$ is indifferent between being
a manager or a worker, $\pi^{\ast}(M,\omega^{\ast}(M))=w^{\ast}(\omega)$, and
is zero otherwise. Note that for any managerial skill $M$, there is only one
type of participant $(M,\omega)$ for which $\phi(M,\omega,\pi^{\ast},w^{\ast
})>0$.

The mass (market supply) of managers of skill $M$, $S^{\ast}(M,\pi^{\ast
},w^{\ast})$ is:%

\begin{equation}
	S^{\ast}(M,\pi^{\ast},w^{\ast})=\phi(M,\omega,\pi^{\ast},w^{\ast}%
	)p_{M_{\omega}}+\sum_{M,\omega}I^{\ast}(M,\omega,\pi^{\ast},w^{\ast
	})p_{M_{\omega}} \label{supply of managers}%
\end{equation}


Let $J^{\ast}(M,\omega)$ be an indicator function which takes the value 1 if a
manager of skill $M$ hires a worker of skill $\omega$ and zero otherwise. The
mass (market demand) for workers of skill $\omega$, $d^{\ast}(\omega,\pi
^{\ast},w^{\ast})$ is:%

\begin{equation}
	d^{\ast}(\omega,\pi^{\ast},w^{\ast})=\sum_{M}J^{\ast}(M,\omega)S^{\ast}%
	(M,\pi^{\ast},w^{\ast}) \label{demand for workers}%
\end{equation}


Let $i^{\ast}(M,\omega,\pi^{\ast},w^{\ast})$ be an indicator function which
takes the value 1 if a participant of skill $(M,\omega)$ strictly prefers to
be a worker and zero otherwise. Let $\Phi(M,\omega,\pi^{\ast},w^{\ast}%
)\in(0,1]$ if a participant of skill ($M,\omega)$ is indifferent between being
a manager or a worker, $\pi^{\ast}(M,\omega^{\ast}(M))=w^{\ast}(\omega)$, and
is zero otherwise. The mass (market supply) of workers of skill $\omega$,
$n^{\ast}(\omega,\pi^{\ast},w^{\ast})$ is:%

\begin{equation}
	n^{\ast}(\omega,\pi^{\ast},w^{\ast})=\Phi(M,\omega,\pi^{\ast},w^{\ast
	})p_{M_{\omega}}+\sum_{(M,w)}i^{\ast}(M,\omega,\pi^{\ast},w^{\ast
	})p_{M_{\omega}} \label{supply of workers}%
\end{equation}


We now define a competitive equilibrium for this labour market:
\begin{definition}
	\begin{enumerate}
		Let $P(M,w)$ be the population supply of skills.
		
		\item A competitive equilibrium is an equilibrium wage function, $w^{\ast}%
		(w)$, such that:
		
		\item All labor market participants choose the occupations which maximize
		their incomes. (i.e, (\ref{occupational choice} is satisfied).
		
		\item All managers choose workers which maximizes their profits according to
		(\ref{profit max}) and (\ref{worker choice}).
		
		\item The market demand for workers is equal to the market supply of workers
		by skills:%
		\begin{equation}
			d^{\ast}(\omega,\pi^{\ast},w^{\ast})=s^{\ast}(\omega,\pi^{\ast},w^{\ast
			}),\omega=\{h,l\} \label{market equilibrium}%
		\end{equation}
		
	\end{enumerate}
\end{definition}

We restrict the population size by type of participants to be decreasing in the skills of the
participants, consistent with commonly observed occupational skills
distributions. 

\begin{assumption}
	(Monotonicity) $p_{Hh}<p_{Hl}<\,p_{Lh}<p_{Ll}$
	\label{monotonicity}
\end{assumption}

\section{Two cases}

	
In addition to Assumption \ref{monotonicity}, Case I ($p_{Hl}\leq p_{Lh}<p_{Hl}+p_{Hh}$) limits the asymmetry in the distribution of occupational individual skills---relax this in Case II and instead consider $p_{Hl} > p_{Lh}<p_{Hl}+p_{Hh}$.

\subsection{Equilibrium}
\begin{proposition}
	\label{p1}A Case I equilibrium exists. The equilibrium earnings function is:%
	\begin{align}
		w^{\ast}(h) &  =\frac{1}{2}R(H,h)\label{Case 1 wage function}\\
		w^{\ast}(l) &  =\frac{1}{2}R(L,l)\nonumber
	\end{align}
	In equilibrium, there are $\frac{p_{Hh}+p_{Lh}+p_{Hl}}{2}$ ($H,h$) firms, and
	($\frac{1}{2}p_{Ll})$ ($L,l$) firms. No mixed occupational skills firm exist.
\end{proposition}

\begin{proof}%
	\begin{align*}
		\pi^{\ast}(H,h)  & =R(H,h)-w^{\ast}(h)=\frac{1}{2}R(H,h)\\
		\pi^{\ast}(H,l)  & =R(H,l)-w^{\ast}(l)=R(H,l)-\frac{1}{2}R(L,l)\\
		\pi^{\ast}(H,h)-\pi^{\ast}(H,l)  & =\frac{R(H,h)-2R(H,l)+R(L,l)}{2}>0
	\end{align*}
	Max supermodularity of the revenue function (\ref{maxsupermodular}) shows that a high skill
	manager, $H$, will strictly prefer to hire a high skill worker, $h$, than a
	low skill worker, $l$. Similarly, a low skill manager, $L$, will strictly
	prefer to hire a low skill worker, $l$, than a high skill worker, $h$.All mixed skill individuals will choose to work in their high skill occupation. Since $p_{Hl}\leq p_{Lh}$, only $p_{Hl}$ ($H,l)$ managers can
	match with their $(L,h)$ worker counterparts. This leaves ($p_{Lh}-p_{Hl})$
	high skill workers to match with a ($H,h$) manager. The rest of the $(H,h)$
	individuals, $p_{Hh}-(p_{Lh}-p_{Hl})$, divided equally between being managers
	and workers, and match with each other. Altogether, there will be
	\[
	p_{Hl}+(p_{Lh}-p_{Hl})+\frac{p_{Hh}-(p_{Lh}-p_{Hl})}{2}=\frac{p_{Hh}%
		+p_{Lh}+p_{Hl}}{2}%
	\]
	high skill firms. Low skill individuals equally divide into being managers and workers, and
	match with each other. Again, max supermodularity of the revenue function will
	show that these low skill managers will not want to match with a high skill
	worker.
\end{proof}


\begin{proposition}
	\label{p2}\bigskip A Case II equilibrium exists. The equilibrium earnings
	function is:%
	\begin{align}
		w^{\ast}(h) &  =R(L,h)-\frac{1}{2}R(L,l)>\frac{1}{2}%
		R(L,l)\label{Case 2 wage function}\\
		w^{\ast}(l) &  =\frac{1}{2}R(L,l)\nonumber
	\end{align}
	Equilibrium profits are:%
	\begin{align}
		\pi^{\ast}(H,h) &  =R(H,h)-w^{\ast}(h)=R(H,h)-R(L,h)+\frac{1}{2}%
		R(L,l)\label{Case 2 profit function}\\
		\pi^{\ast}(L,l) &  =R(L,l)-\frac{1}{2}R(L,l)=\frac{1}{2}%
		R(L,l)\label{Ll profit}%
	\end{align}
	
\end{proposition}

\begin{proof}
	Case II considers the case where there is enough high skilled workers from
	mixed skilled individuals to match with than high skilled managers from high
	skilled and mixed skilled individuals. To effect such an equilibrium, high
	skilled individuals have to choose to be managers. Due to
	(\ref{Case 2 wage function}), (\ref{Case 2 profit function}) and max
	supermodularity of the revenue function, (\ref{maxsupermodular}),
	\[
	\pi^{\ast}(H,h)-w^{\ast}(h)=R(H,h)+R(L,l)-R(L,h)-R(L,h)>0.
	\]
	The above shows that managerial profit of high skill managers exceeds the
	wages of high skill workers implying that all $(H,h)$ participants will choose
	to be managers.	Because wages of high skill workers are higher than low skill managers, all $(L,h)$ participants will be workers. $p_{Hh}$ of them will match with the $(H,h)$ managers. Even in this case, some
	high skill workers from ($\mu L,h)$ individuals will have to match with low
	skill managers. I.e. high skill workers must be paid the same no matter who
	they are matched with. The profit of a low skill manager with a high skill
	worker is:%
	\begin{equation}
		\pi^{\ast}(L,h)=R(L,h)-w^{\ast}(h)=R(L,h)-R(L,h)+\frac{1}{2}R(L,l)=\frac{1}%
		{2}R(L,l)\label{Lh profits}%
	\end{equation}
	Which is the equilibrium profit of a low skill manager matched with a low skill worker, (\ref{Ll profit}).So $(L,l)$ managers are fine with matching with high skill workers. Half the remaining $(L,l)$ individuals will become managers and workers respectively, and match with each other. High skill managers will not choose to match with low skill workers:%
	\[
	\pi^{\ast}(H,h)-\pi^{\ast}(H,l)=R(H,h)-R(L,h)+R(L,l)-R(H,l)>0
	\]
	Thus, we have found an equilibrium in Case II.
\end{proof}

\subsection{Characterizing the identified set}
	
	
%	\newpage
%	\bibliographystyle{plainnat}
%	\bibliography{/home/selliott/Research/bib/matching}
	
\end{document}
